Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-09 paper/paper.tex
loop complement \lcomp operator.
loopcomp name update.
fixed loop complement spacing.
loop complements

% Maths operators
\newcommand{\paths}{\operatorname{paths}}
\newcommand{\lessnonind}[1]{\prescript{}{#1}{\rightarrowtail}\ }
\newcommand{\lessind}[1]{\prescript{}{#1}{\hookrightarrow}\ }
\newcommand{\lessmap}[1]{\prescript{}{#1}{\mapsto}\ }
\newcommand{\lesspreceq}[1]{\prescript{}{#1}{\preceq}\ }
\newcommand{\V}{\operatorname{V}}
\newcommand{\N}{\operatorname{N}}
\newcommand{\nds}{\operatorname{S}}
% to do comments
\usepackage{color}
\newcommand{\todo}[1]{{\color{red} {?? [}{#1}{]}}}

@@

The \emph{complement} of a graph $P$ is the graph $\bar{P}~$.  Adjacent vertices in $P$ are
non-adjacent in $\bar{P}$ while non-adjacent vertices in $P$ are adjacent in $\bar{P}$. The
following proposition follows directly from the definitions.

\begin{proposition}\label{prop:comp}
Let $i$ be an assignment of $T$ vertices to $P$ vertices.  Then $i$ satisfies the definition of $P
\hookrightarrow T$ if and only if $i$ satisfies both the definition of $P \rightarrowtail T$ and
of $\bar{P} \rightarrowtail \bar{T}$.
Similarly, $i$ satisfies the definition of $P
\lessind{k} T$ if and only if $i$ satisfies both the definition of $P \lessnonind{k} T$ and of
$\bar{P}
\lessnonind{k} \bar{T}$.
\end{proposition}

>>>>

% Maths operators
\newcommand{\paths}{\operatorname{paths}}
\newcommand{\lessnonind}[1]{\prescript{}{#1}{\rightarrowtail}\ }
\newcommand{\lessind}[1]{\prescript{}{#1}{\hookrightarrow}\ }
\newcommand{\lessmap}[1]{\prescript{}{#1}{\mapsto}\ }
\newcommand{\lesspreceq}[1]{\prescript{}{#1}{\preceq}\ }
\newcommand{\V}{\operatorname{V}}
\newcommand{\N}{\operatorname{N}}
\newcommand{\nds}{\operatorname{S}}
\newcommand{\loopcomp}[1]{\overset{\multimap}{#1}}
% to do comments
\usepackage{color}
\newcommand{\todo}[1]{{\color{red} {?? [}{#1}{]}}}

@@

The \emph{complement} of a (simple) graph $P$ is the graph $\bar{P}~$.  Adjacent vertices in $P$ are
non-adjacent in $\bar{P}$ while non-adjacent vertices in $P$ are adjacent in $\bar{P}$.  The \emph{loop complement} of a graph $P$ is the graph $\loopcomp{P}$.  The constructcion of $\loopcomp{P}$ is similar to that of $\bar{P}~$, however whenever a vertex has a loop in $P$ it does not in $\loopcomp{P}$ and vice versa.  When solving an induced subgraph isomorphism problem we make use of the loop complement; we care about mapping vertices with loops to vertices with loops, and edges without loops to vertices without loops.  (Although when we filter by paths we make use of the complement rather than the loop complement.)  The following proposition follows directly from the definitions.

\begin{proposition}\label{prop:comp}
Let $i$ be an assignment of $T$ vertices to $P$ vertices.  Then $i$ satisfies the definition of $P
\hookrightarrow T$ if and only if $i$ satisfies both the definition of $P \rightarrowtail T$ and
of $\loopcomp{P} \rightarrowtail \loopcomp{T}$.
Similarly, $i$ satisfies the definition of $P
\lessind{k} T$ if and only if $i$ satisfies both the definition of $P \lessnonind{k} T$ and of
$\loopcomp{P}
\lessnonind{k} \loopcomp{T}$.
\end{proposition}
